---
title: "PREDICT_ocpu_server"
author: "gmp26@cam.ac.uk"
date: "19/12/2019"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(devtools)
library(opencpu)
install_github("gmp26/v22")
```

## Starting the server

Start the opencpu server with the v22 package containg the v2.2
PREDICT model

The following chunk will run continuously, serving the PREDICT model as JSON.
Once running, try browsing: 
http://localhost:5656/ocpu/library/
http://localhost:5656/ocpu/library/v22/info
http://localhost:5656/ocpu/library/v22/man/
http://localhost:5656/ocpu/library/v22/man/v22_model/text
http://localhost:5656/ocpu/library/v22/man/wrap_v22_model/text
http://localhost:5656/ocpu/library/v22/R/v22_model/print
http://localhost:5656/ocpu/library/v22/R/wrap_v22_model/print
```{r opencpu}
opencpu::ocpu_start_server()
```
To call the model, send a POST request with inputs in the data from a terminal
```
curl -d'age.start=56' http://localhost:5656/ocpu/library/v22/R/wrap_v22_model
```
This will generate a response with temporary result URLs on the server. Call these URLs 
to retrieve information about the call and its results.
For example, if the response to the POST was
```
/ocpu/tmp/x0b06b1e379c4e0/R/.val
/ocpu/tmp/x0b06b1e379c4e0/R/wrap_v22_model
/ocpu/tmp/x0b06b1e379c4e0/stdout
/ocpu/tmp/x0b06b1e379c4e0/source
/ocpu/tmp/x0b06b1e379c4e0/console
/ocpu/tmp/x0b06b1e379c4e0/info
/ocpu/tmp/x0b06b1e379c4e0/files/DESCRIPTION
```
then 
```
curl http://localhost:5656/ocpu/tmp/x0b06b1e379c4e0/stdout
``` 
will retrieve the results as JSON.

To access a more readable but less computer friendly result, use the unwrapped version:
```
curl -d'age.start=56' http://localhost:5656/ocpu/library/v22/R/v22_model
```
and retrieve results from the printed returned value
```
curl http://localhost:5656/ocpu/tmp/xxxxxxxxxxxxxx/R/.val/print
```




